Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2019-12-13 paper/manuscript.tex
Updates from Overleaf

\todo[inline,color={green!20}]{ASJSM: Discuss implications of the SAMPL6 SAMPLing paper~\cite{rizzi2019sampl6} on reproducibility between simulation packages and potential sensitivity to other calculation details. @jmichel, @dmobley}

>>>>

\todo[inline,color={green!20}]{ASJSM: Discuss implications of the SAMPL6 SAMPLing paper~\cite{rizzi2019sampl6} on reproducibility between simulation packages and potential sensitivity to other calculation details. @jmichel, @dmobley}
Finite computing resources necessarily limit the generated number of uncorrelated samples of potential energy surfaces, and therefore alchemical free energy calculations only give free energy estimates to within given precision. An important consideration is how reproducible alchemical free energy calculation are in practice. In simple cases such as absolute hydration free energies of small organic molecules, or relative hydration free energy calculations between structurally similar organic molecules it should be possible to obtain highly precise estimates with a given software package (with a sample standard deviation under 0.01 kcal/mol). For more complex use cases such as protein-ligand binding free energies the repeatability is often substantially worse. A good practice is to perform two or three runs of the same perturbation to assess repeatability with a given protocol. The sample standard deviation will give a crude estimate of the reliability of the estimates, and whether the precision is sufficient for the problem at hand. Where this is practical, a more stringent test is to use different input coordinates for each repeat run.Note that these issues concern calculations carried out with a single software package. The issue of reproducibility of free energy calculations across different simulation packages has attracted attention recently. Greater variability is expected due to methodological differences such as integrators, thermostats, barostats, treatment of long-range electrostatics. For absolute and relative hydration free energies of small organic molecules a variability of ca. 0.2 kcal/mol between popular simulation packages has been reported.(REF Reproducibility of hydration free energies Loefler et al.  JCTC 2018) In recent SAMPL6 SAMPLing challenge a larger variability of 0.3 to 1.0 kcal/mol was noted in the computed absolute binding free energies of host/guest systems even though similar input and simulation parameters were used (Ref Rizzi et al SAMPLing biorxiv). Further work is needed to ensure reproducibility of alchemical free energy calculations across implementations to guarantee that force-field development efforts lead to transferable potential energy functions.
